Privacy-Preserving Localisation Using Private Linear-Combination Aggregation

### 2020-11-11 main.tex
One more read-through of intro with couple small changes Also update to leakage honest-but-curious section specifying example of why its used

\subsection{Notation}
Throughout this work, we will use the following notation. Lowercase underlined characters are vectors, $\vec{a}$, and random variables are bold, $\rv{a}$. Uppercase bold characters are matrices, $\mat{A}$, with $\mat{A}^{-1}$ denoting the inverse and $\mat{A}^\top$ the transpose. $|a|$ is the absolute value of $a$ and $\lVert\vec{a}\rVert$ the vector normal. Subscripts $\rv{x}_{k|j}$ will denote an estimate of $\rv{x}_k$ using measurements from times up to and including $j$. $\E{\cdot}$ and $\Var{\cdot}$ are used for the expected value and variance, respectively, and encryption and decryption with key $k$ are denoted $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$. Additionally, key $k$ may be ommited when inferrable from context. $\lfloor\cdot\rceil$ rounds to the nearest integer, $a\|b$ stands for a bitwise concatenation of $a$ and $b$ and sets will be written as $\{\dots\}$ while ordered sequences as $\langle\dots\rangle$.

@@

Bayesian approaches can achieve better accuracy due to their exploitation of process dynamic knowledge. In \cite{aristovEncryptedMultisensorInformation2018}, partially homomorphic encryption is used to encrypt measurement information and produce location estimates at a navigator. While producing estimate errors and requiring only uni-directional communication, this method exclusively supports linear measurement models and is therefore not suitable for range-only measurements. Encrypted model predictive control methods \cite{farokhiPrivacyDynamicalSystems2020} also introduce some privacy-preserving methods relevant to estimation. \cite{alexandruEncryptedCooperativeControl2019} proposes secure distributed control input aggregation using a novel weighted sum aggregation scheme, but requires a repeated, slow, key distribution among all involved parties. In \cite{farokhiSecurePrivateControl2017}, a secure cloud-based control aggregator using partially homomorphic encryption is proposed, but is suitable only for untrusted service-providing cloud architectures and handles only the aggregation step homomorphically, making its application to localisation impractical.

@@

\subsection{Leakage} \label{subsec:leakage}
With the algorithm defined, we can analyse the localisation leakage when the strictly defined LCAO leakage is taken into account. We recall the assumptions on participant capabilities made in Section \ref{subsec:capabilities}. Global and consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage. Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining prior knowledge about remaining sensor measurements, which may be achievable by detecting changes in real measurements after reporting false ones. As misbehaving sensors are also a known problem which complicates homomorphic operations, active malicious sensors are not considered in the scope of this work.

>>>>

\subsection{Notation}
Throughout this work, we will use the following notation. Lowercase underlined characters are vectors, $\vec{a}$, and random variables are bold, $\rv{a}$. Uppercase bold characters are matrices, $\mat{A}$, with $\mat{A}^{-1}$ denoting the inverse and $\mat{A}^\top$ the transpose. $|a|$ is the absolute value of $a$ and $\lVert\vec{a}\rVert$ the vector normal. Subscripts of the form $\rv{x}_{k|j}$ will denote an estimate of $\rv{x}_k$ using measurements from times up to and including $j$. $\E{\cdot}$ and $\Var{\cdot}$ are used for the expected value and variance, respectively, and encryption and decryption with key $k$ are denoted $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$. Additionally, key $k$ may be ommited when inferrable from context. $\lfloor\cdot\rceil$ rounds to the nearest integer, $a\|b$ stands for a bitwise concatenation of $a$ and $b$ and sets will be written as $\{\dots\}$ while ordered sequences as $\langle\dots\rangle$.

@@

Bayesian approaches can achieve better accuracy due to their exploitation of process dynamic knowledge. In \cite{aristovEncryptedMultisensorInformation2018}, partially homomorphic encryption is used to encrypt measurement information and produce location estimates at a navigator. While producing estimate errors and requiring only uni-directional communication, this method exclusively supports linear measurement models and is therefore not suitable for range-only measurements. Encrypted model predictive control methods \cite{farokhiPrivacyDynamicalSystems2020} also introduce some privacy-preserving methods relevant to estimation. \cite{alexandruEncryptedCooperativeControl2019} proposes secure distributed control input aggregation using a novel weighted sum aggregation scheme, but requires a repeated, slow, key distribution step among all involved parties. In \cite{farokhiSecurePrivateControl2017}, a secure cloud-based control aggregator using partially homomorphic encryption is proposed, but is suitable only for untrusted service-providing cloud architectures and handles only the aggregation step homomorphically, making its application to localisation impractical.

@@

\subsection{Leakage} \label{subsec:leakage}
With the algorithm defined, we can analyse the localisation leakage when the strictly defined LCAO leakage is taken into account. We recall the assumptions on participant capabilities made in Section \ref{subsec:capabilities}. Global and consistent broadcasting is in line with the LCAO definition and required to guarantee the scheme's leakage. Honest-but-curious sensors are not required for scheme privacy, but avoid the possibility of malicious sensors gaining knowledge about other sensors' measurements, when navigator behaviour is dependant on its estimate. This may be achievable by detecting changes in measurements after reporting false ones. As misbehaving sensors are also a known problem which complicates homomorphic operations, active malicious sensors are not considered in the scope of this work.
